target_offtarget

### 2025-01-31 manuscript_figures.Rmd
Update kobu and cardio supp figs

ggsave("figures/manuscript_figure_2025/PNG/Figure_3.png", 
       width = 10, height = 8)
```
### --------------------

### Figure S10

@@

@@

ggsave("figures/manuscript_figure_2025/PNG/Figure_S12.png",
       width=12,
       height=10)
```

>>>>

ggsave("figures/manuscript_figure_2025/PNG/Figure_3.png", 
       width = 10, height = 8)
```
### .........................
### .........................

### ----Genome medicine results----
### Figure S10

@@

```
### --------------------

@@

ggsave("figures/manuscript_figure_2025/PNG/Figure_S12.png",
       width=12,
       height=10)
```
### .........................

### ----Kobuvirus / Cardiovirus results----

#### Figure S13

```{r}

kobu_depth <-
  read.table(
    "data_kobuvirus/kobuvirus_TE_polyomics_readdepth_20241007.tsv",
    sep = "\t",
    header = TRUE
  ) %>%
  select(!expt) %>%
  select(!Number.of.paired.end.reads..QT.)

cardio_depth <-
  read.table(
    "data_cardiovirus/cardiovirus_denovo_bowtie2_read_depth_per_sample_dedup.tsv",
    sep = ",",
    header = TRUE
  )

depth_both <- rbind(kobu_depth, cardio_depth)

depth_both$type <- depth_both$type %>%
  case_match("dedup_TE" ~ "dedup",
             .default = depth_both$type)

coverage_labels <- c(
  "k97_19971" = "Kobuvirus",
  "cardiovirus" = "Cardiovirus",
  "p2" = "P1",
  "p8" = "P2"
)

#### *** Final plot ***
```{r}

depth_both |>
  filter(Background != "p6") |>
  filter(type == "dedup") |>
  filter(mapper == "bowtie2") |>
  filter(Viral.load != "NA") |>
  ggplot(aes(
    x = Viral.load,
    y = (mean_depth),
    colour = Background
  )) +
  geom_point() +
 theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "none", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +  
  facet_grid(Background ~ virus, labeller = as_labeller(coverage_labels)) +
  scale_color_manual(values = cols2) +
  ylab("Mean read depth") +
    xlab("Spike-in viral load (gc/ml)") +

   scale_x_log10(labels = scales::trans_format("log10",
                                              scales::label_math())) + 
  scale_y_log10(labels = scales::trans_format("log10",
                                              scales::label_math()))

ggsave("figures/manuscript_figure_2025/PDF/Figure_S13.pdf",
       width=8,
       height=4)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S13.png",
       width=8,
       height=4)

#### Figure S14

```{r}

kobu_per_site <-
  read.table(
    "data_kobuvirus/kobuvirus_TE_polyomics_readdepth_persite_20241007.tsv",
    sep = "\t",
    header = TRUE
  ) %>%
  select(virus,
         seg,
         site,
         coverage,
         n_sites,
         Sample_id,
         Background,
         Viral.load,
         mapper,
         type)

kobu_per_site$Viral.load <- 
  kobu_per_site$Viral.load %>%
  replace_na(., 0)

kobu_per_site$Sample_id <- kobu_per_site$Sample_id %>%
  case_match("RNA-Msp-p2" ~ "P1",
             "RNA-Msp-p8" ~ "P2",
             .default = kobu_per_site$Sample_id)

kobu_per_site$Background <- kobu_per_site$Background %>%
  case_match("p2" ~ "P1",
             "p8" ~ "P2",
             .default = kobu_per_site$Background)

cardio_per_site <-
  read.table(
    "data_cardiovirus/cardiovirus_denovo_bowtie2_read_depth_per_site_and_sample_dedup.tsv",
    sep = ",",
    header = TRUE
  )

cardio_polyomics_per_site <-
  read.table(
    "data_cardiovirus/cardiovirus_denovo_bowtie2_readdepth_per_site_sample_dedup_polyomics.tsv",
    sep = ",",
    header = TRUE
  ) %>%
  select(!contig_name)

#View(cardio_polyomics_per_site)

cardio_TE_polyomics <-
  full_join(
    cardio_per_site,
    cardio_polyomics_per_site,
    by = c(
      "virus",
      "seg",
      "site",
      "coverage",
      "n_sites",
      "Sample_id",
      "Background",
      "Viral.load",
      "mapper",
      "type"
    )
  )

cardio_TE_polyomics$Viral.load <- cardio_TE_polyomics$Viral.load %>%
  replace_na(., 0)

drops <-
  c(
    "RNA-Msp-p1",
    "RNA-Msp-p3",
    "RNA-Msp-p4",
    "RNA-Msp-p5",
    "RNA-Msp-p6",
    "RNA-Msp-p7",
    "RNA-Msp-p9"
  )

cardio_TE_polyomics <- cardio_TE_polyomics %>%
  filter(!Sample_id %in% drops)

cardio_TE_polyomics$Sample_id <- cardio_TE_polyomics$Sample_id %>%
  case_match("RNA-Msp-p2" ~ "P1",
             "RNA-Msp-p8" ~ "P2",
             .default = cardio_TE_polyomics$Sample_id)

cardio_TE_polyomics$Background <- cardio_TE_polyomics$Background %>%
  case_match("S18" ~ "P1",
             "S43" ~ "P2",
             "p2" ~ "P1",
             "p8" ~ "P2",
             .default = cardio_TE_polyomics$Background)

persite_both <- rbind(kobu_per_site, cardio_TE_polyomics)

persite_both$type <- persite_both$type %>%
  case_match("dedup_TE" ~ "dedup",
             "dedup_polyomics" ~ "dedup",
             .default = persite_both$type)

#TE data only - compare coverage between backgrounds/viral loads

coverage_labels <- c(
  "100" = "10^{2}",
  "1000" = "10^{3}",
  "100000" = "10^{5}",
  "0" = "Shotgun",
  "Kobuvirus" = "Kobuvirus",
  "Cardiovirus" = "Cardiovirus"
)

coverage_labels2 <- c(
  "100" = "10^{2}",
  "1000" = "10^{3}",
  "100000" = "10^{5}",
  "0" = "Shotgun",
  "A" = "A",
  "B" = "B",
  "C" = "C",
  "D" = "D",
  "F" = "F",
  "G" = "G",
  "H" = "H",
  "I" = "I",
  "J" = "J",
  "K" = "K",
  "L" = "L",
  "M" = "M",
  "N" = "N",
  "O" = "O",
  "P" = "P",
  "ME_P1" = "P1",
  "ME_P2" = "P2"
)

kobu_coverage <- kobu_per_site %>%
  filter(mapper == "bowtie2") %>%
  filter(type == "dedup") %>%
  filter(Background != "p6") %>%
  group_by(Sample_id, Viral.load, Background) %>%
  filter(coverage > 0) %>%
  summarise(genome_coverage = n()) %>%
  mutate(percent_coverage = genome_coverage / 8467) %>%
  mutate(virus = "Kobuvirus")

cardio_coverage <- cardio_TE_polyomics %>%
  filter(Background != "p6") %>%
  group_by(Sample_id, Viral.load, Background) %>%
  filter(coverage > 0) %>%
  summarise(genome_coverage = n()) %>%
  mutate(percent_coverage = genome_coverage / 6945) %>%
  mutate(virus = "Cardiovirus")

coverage_both <- rbind(kobu_coverage, cardio_coverage)

coverage_both$Viral.load <- factor(coverage_both$Viral.load, labels = c("Shotgun",
    "10^{2}", 
    "10^{3}", 
    "10^{5}"
    ))

#### *** Final plot ***
```{r}

coverage_both %>%
  ggplot(aes(x = Sample_id, y = percent_coverage, color = Background)) +
  geom_point() +
  ylab("Genome coverage") +
  xlab("Sample ID") +
  facet_grid(virus ~ (Viral.load),
             scales = "free_x",
             label = label_parsed) +
  scale_color_manual(values = cols2, labels = c("P1", "P2")) +
 theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "right", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) + 
  scale_y_continuous(limits = c(0, 1))

#PDF
ggsave("figures/manuscript_figure_2025/PDF/Figure_S14.pdf", 
       width = 8, 
       height = 4)

#PNG
ggsave("figures/manuscript_figure_2025/PNG/Figure_S14.png", 
       width = 8, 
       height = 4)

#### Figure S15

#per site genome coverage - Kobu

persite_both$Viral.load <- factor(persite_both$Viral.load, labels = c("Shotgun",
    "10^{2}", 
    "10^{3}", 
    "10^{5}"
    ))

persite_both$Viral.load <- factor(persite_both$Viral.load, levels = c(
    "10^{2}", 
    "10^{3}", 
    "10^{5}",
    "Shotgun"
    ))

persite_both |>
  filter(virus == "k97_19971") |>
  filter(mapper == "bowtie2") |>
  filter(type == "dedup") |>
  filter(Background != "p6") |>
  ggplot(aes(
    x = site,
    y = (coverage),
    fill = Background
  )) +
  geom_col() +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "right",
    panel.grid.major = element_line(linewidth = 0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth = 0.1, color = "lightgray")
  ) +   
  facet_wrap(Viral.load ~ Sample_id, labeller = label_parsed) +
  scale_fill_manual(values = cols2, labels = c("P1", "P2")) +
  ylab("Coverage") +
  xlab("") +
  ggtitle("Kobuvirus") +
  scale_y_log10(labels = scales::trans_format("log10",
                                              scales::label_math()))

#### *** Final plot ***
```{r}
#PDF
ggsave("figures/manuscript_figure_2025/PDF/Figure_S15.pdf",
       width=12,
       height=7)

#PNG
ggsave("figures/manuscript_figure_2025/Png/Figure_S15.png",
       width=12,
       height=7)

#### Figure S16
```{r, echo=FALSE, warning=FALSE, message=FALSE}

#per site genome coverage - Cardio

persite_both |>
  filter(virus == "cardiovirus") |>
  filter(mapper == "bowtie2") |>
  filter(type == "dedup") |>
  filter(Background != "p6") |>
  ggplot(aes(
    x = site,
    y = coverage,
    fill = Background
  )) +
  geom_col() +
  facet_wrap(Viral.load ~ Sample_id, labeller = label_parsed) +
  scale_fill_manual(values = cols2, labels = c("P1", "P2")) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "right",
    panel.grid.major = element_line(linewidth = 0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth = 0.1, color = "lightgray")
  ) +
  ylab("Coverage") +
  xlab("") +
  ggtitle("Cardiovirus") +
  scale_y_log10(labels = scales::trans_format("log10",
                                              scales::label_math()))
```

#### *** Final plot ***
```{r}

#PDF
ggsave("figures/manuscript_figure_2025/PDF/Figure_S16.pdf",
       width=12,
       height=7)

#PNG
ggsave("figures/manuscript_figure_2025/PNG/Figure_S16.png",
       width=12,
       height=7)
```
